使用贝叶斯推断方法探测隐藏敌人单位探测

### 2018-04-24 paper_ch.tex
remove comparing english

@@

Assuming a location which have samller distance to two conflict factions have higher probability causing a battle,
how do we infer the location of enemy if we can only observe the locations of allies and battles? 
The latent variable inference problem requieres a suitable front probability model and a effiecent way to run the 
inference. In this work, a battle model is introduced and a bayes inference framework based on pytorch 
is developed to reach the inference task including point, movement detection and 
exist probability estimation with different prior and various initialization value setting.
A case study about The battle of Gettysburg is included to show the overview of the content covered by the paper.

@@

In real warfare, you can't observe enemy units even allies units as RTS or classic board wargame way.
The only thing you can rely on are complex and confusing even self-contradiction information and misinformation.
There're a lot of example, that general misunderstand information and may be defeated due to this. 
Bing Sun manipulated field kitchen of his army to trick his opponent, General McClellan reject to attack
due to "peace gun"(fake gun instrument) seted by south rebels, lossing oppotunity to beat rebel down.

Unfortunately, current military decision similation program, 
such as "classic" wargame (a example see Figure~\ref{fig:hps}) and somewhat  "serious" RTS, 
tend to capture more "macro" aspect and simplify the reconnaissance and 
information modeling aspect into a unaccepted level.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{SmolenskR4.jpg}
\caption{This figure show the reconnassance treatment of Smolensk' 41, 
a classic hex wargame developed by HPS.
Units can only be observed wholly or can't be observed.
图中展示了经典兵棋公司HPS的作品斯摩棱斯克41对侦查的处理——单位仅能出于完全可知和完全不可知的状态。 }
\label{fig:hps}
\end{figure}

Though we can read the oob(order of battle) as Figure~\ref{fig:metz} from map of battle, 
but it's obvious that those marks are placed in there using post Liang Zhuge information. 
In real time battle field, you can only hear where be attacked and where observe the trace of enemy 
(instead of unit detail id or somewhat weird strange quatity information), 
and some of them may be wrong and some of them may be released by enemy to confuse you.
The movement of Jackson in valley campaign is a vivid example about how the fake information intentionally
made by oppnent get the change to weaken the strength of army.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{metz.jpg}
\caption{The map of battle of Metz, showing oob that can't be observed in real time battlefied.
梅兹战役地图，地图展示了并不应该在真实战场上所能看到的OOB }
\label{fig:metz}
\end{figure}

There are some work were made to solve this problem 
\cite{hostetler2012inferring} \cite{vsmejkal2016integrating} \cite{touhou}.
Since they filter small part of information from replay file, they made a case that enemy can not be 
seen in that direct way, then they proposed according probability model to rebuild real situation.
Those're good tries, but not real demands for most of case. The paper we
\footnote{Though the paper only have a writer, 
but "we" seems a traditional and kind pronoun for such paper. 
In following content, both "we" and "I" will be used to represent the writer.} 
wrote will deal the problem in a more direct and intuitive way. 
A coordinate based position and movement detecting method is present in this paper.

@@

In forward model, a process that can give probility of number of battles and the mass in support space 
is required. For example, given ally and ememy location setting as Figure~\ref{fig:stateNoBattle}.

@@

\begin{figure}[ht]
\includegraphics{state_no_battle.png}
\caption{Ally and enemy setting
友军和敌军的位置设定}
\label{fig:stateNoBattle}
\end{figure}

Suppose the the number of battle is $10$ 
\footnote{ Though the number can modeled as it draw from a given distribution by adding 
stochastic process, it be not adpoted due to its extra difficulty in express.}
, we can model the $10$ battles are indepently drawn from below distribution:

@@

Where $p^A_{i}(x,y)$ indicate the probability density "released" from of i’st ally unit,
$p^E_{j}$ indicate same thing from j’st enemy unit. And the density is defined by:

@@

Where the probability in $(x,y)$ released from i'th unit of S side($S \in \{A,E \}$). 
So the above formula can be rewritten as:

@@

Where $nearst(x,y)$ point to the unit(enemy or ally) which is nearest to (x,y).

This means the non-normalized probability is only subject to the nearest two conflict units’s distance. 
Though the assumption don’t have abundant meaning,
it capture something crucial but have obvious weakness such as independent hypothesis, 
lately the model will be adujusted mutiple times to resolve this and other problems. 
Anyway, the probability can be computed and visualized as contour Figure~\ref{fig:stateNoBattleProb}.

@@

\begin{figure}[ht]
\includegraphics{state_no_battle_prob.png}
\caption{Battle density distribution 战役发生概率密度分布}
\label{fig:stateNoBattleProb}
\end{figure}

The probability distribution don't have a standard shape, implying it's hard to sample. 
To overcome this, the "grid sampling" technology is used. In this example,
 the support of density is limited to $[-1,5] \times [0,6]$
(that is, the point out of set $[-1,5] \times [0,6]$ have zero density). 
And $100 \times 100$ points are selected to build a grid approxmation. 
See a size-reduced example serve to eye in Figure~\ref{fig:gridify}.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{gridify.png}
\caption{$25 \times 25$ discrete approxmation 离散近似}
\label{fig:gridify}
\end{figure}

So firstly we draw a square in the grid according to the approximated probability, 
and then draw two uniform variable $dX \sim U(0,5-(-1)/100),dY \sim U(0,(6-0)/100)$ 
to determine the position drew by this process.

Repeating the process 10 times, 
we can get size 10 independent sample from the distribution as such Figure~\ref{fig:stateSampleBattle}.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{state_sample_battle.png}
\caption{Ally,enemy,prob, and a sample of battle 敌友军，战役概率与一个特定战役样本}
\label{fig:stateSampleBattle}
\end{figure}

If the positions of enemy is hidden, 
then we can get a instance of problem data as Figure~\ref{fig:stateNoEnemy}.

这时如果把敌人的位置隐去，就可以得到实际推断中所用的数据，如图~\ref{fig:stateNoEnemy}。
如频率主义稻草人式讨论，可以通过比较生成过程隐去的真实值与推断的值来判定推断的效能。

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{state_no_enemy.png}
\caption{hide enemy 隐藏敌人后，实际推断时所能看到的信息}
\label{fig:stateNoEnemy}
\end{figure}

@@

Although the distribution may satisfy our goal, 
but the $\min$ function will make that gradient-based optmization method difficult to effect 
in those units whose is not nearest to observed battle. 
So a another specification is proposed below to get it done:

First, a differentiable classifier is used to determine the "conflict level" in every point.
Supposing a point is more likely be controled by S side 
if a unit of S side have shortest distance to it, then we can define that the more two control probability 
being close to eachother, the more conflict chance in this point. So the conflict factor is defined by:

@@

Where $P_\text{ally}(x,y)$ indicate the probability(belief) of $(x,y)$ being classified 
into ally set given by classifer.

In this paper, we use naive bayes classifer as classifer since it helps gradient computation. 
The classification probability are given by:

@@

Where $N(x \mid \mu,\sigma)$ is normal probability density function:

@@

The classifier parameters $\mu,\sigma$ are estimated by normal moment estimation.

@@

Where $Z \in \{ X,Y \}$ and $S \in \{ A,E \}$. $N_S$ is number of units of side $S$.

A living example of classify probability can be seen in Figure~\ref{fig:naivebayes}.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{naivebayes.png}
\caption{naive bayes predict probability coutour map 朴素贝叶斯分配器预测概率等高线图}
\label{fig:naivebayes}
\end{figure}

Then, we define that the less the distance between point and any units(ally or enemy) be,
the more likely the point will occur a battle.

@@

Where $u$ means any unit. $\min_u distance$ the shortest distance in all possible distance 
between coordinate of unit and $(x,y)$.

So the probability is:

@@

Set $\alpha=0.1$, the 2d function can be seen in Figure~\ref{fig:combOne}:

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb1.png}
\caption{Combining a naive bayes classifier and a smooth distance factor
组合朴素贝叶斯分类器与平滑的距离因子后的战斗概率}
\label{fig:combOne}
\end{figure}

The smooth probability seems good, but the sampled result seems too diffused 
(see Figure~\ref{fig:combTwo}) and if scale is enlarged, 
the problem even worsen (see Figure~\ref{fig:combThree}).
Some parameters tuning are tried but not satisfy the demand. 
So the smooth function family are removed and uniform distribution is employed.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb2.png}
\caption{Too diffused sample 过于分散的样本}
\label{fig:combTwo}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb4.png}
\caption{When extend the scale, unrational sample will present inevitably.
当扩大讨论范围后，不合理的样本不可避免地出现}
\label{fig:combThree}
\end{figure}

\subsection{Empolyed setting}

We assign a point constant probability 
if it is greater than conflict threshold and less than distance threshold:

@@

Figure~\ref{fig:combFive} shows how the unrational sample point is suppressed by the way.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb5.png}
\caption{Forced 0 zero probability can suppress the unrational point
强制0概率可以解决不合理点的麻烦}
\label{fig:combFive}
\end{figure}

To get gradient information to proceed optimization, 
rewrite the conditional jump function to "soft" version, 
just like relation of ReLu and softplus in machine learning. 
For example, sigmmoid function $sigm(x) = \frac{1}{1+\exp(-x)}$:

@@

Where $t$ is "tense" parameter controling the shape of sigmoid, $\theta_0,\theta_1$ are threshold for
conflict level and distance. For $\theta_0=0.2,\theta_1=1.5,t = 10.0$, the result can be show in Figure~\ref{fig:combSix}.

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb6.png}
\caption{Selected model 基线模型}
\label{fig:combSix}
\end{figure}

The model seems perfect to our demand, following article will use it as baseline model.

@@

A bayes inference framework is a programming language or a library that is made to organize the 
programming for model and inference related optmization code.

@@

There're a lot of inference framework such as Stan \cite{carpenter2017stan}, 
pymc\cite{patil2010pymc} and edward \cite{tran2016edward}. 
The core of them are a automated gradient computation library, 
they're stan-math, theano, tensorflow respectively.

Nevertheless, those except stan are too weak in their ability describing complex probabiliy function.
And the compile time of stan is too long. 
So a light-weight bayes inference library is proposed to fulfill our goal. 
The framework is based on pytorch providing a flexible automated gradient computation lib and 
easy-to-use dynamic computation graph like Chainer.

@@

In this section, three inference method used below sections will be introduced.

@@

Maximum A Posteriori(MAP) is a estimator that maximize the likelihood function 
coporating prior information. Since the task of gradient computation is done by pytorch, 
we can only call the SGD or any other artful NN(neural net)-oriented optimizer to do standard gradient 
descent (take $loss = -likelihood \times prior$) process. See Algorithm~\ref{alg:sgd}.

@@

Variational inference use simple joint distribution setting to approximate complex 
exact posterior distribution, using Kullback-Leibler(KL) diversity as optimizing target \cite{blei2017variational}. That is:

@@

Where $p(\theta \mid x)$ is exact posterior distribution. 
$q(\theta)$ is corresponding variational distribution approximating the exact one.
The family of $q(\theta)$ are usually employed as normal distribution, especially $N(\mu,\mathbf{\sigma})$ form.
If $\mathbf{\sigma}=\mathrm{diag}(exp(\mathbf{\omega}))$, 
that is so called meanfield setting we will see it in following content.
%$q(\theta \mid \mu,\omega)$ is corresponding variational distribution approximating the exact one
%and the $\mu,\omega=\log(\sigma)$ means the distribution is in normal family with independent variable(meanfield).
%The $\mu,\omega$ will be omited in following content.

Since it employ variational(approximated) distribution $q(\theta)$ as expectation weight 
instead of exact posterior distribution,
the computation difficulty is relative reduced. But it seems too hard to deal too. 
So we turn to considering evidence lower bound(ELBO) which is lower bound for $\log p(x)$:

@@

The relation of KL diversity and ELBO can be show:

@@

So we can maximizing ELBO to minimizing KL diversity. 
To do the optimization, the tradition variational inference method, 
Coordinate ascent variational inference (CAVI) algorithm,
require a analytic conditional expectation $E_{-j}(\log p(\theta_j \mid \mathbf{\theta}_{-j},\mathbf{x}))$. 
It's annoy when lazy statistician aware that he can do sampling to
reach same goal without any of such brain exhausted brain challenges.

The Automatic differentiation variational inference (ADVI) is presented by 
\cite{kucukelbir2017automatic} and \cite{kucukelbir2014fully} to fix it. 
The core of the algorithm is to use random integral to approximate a hard-to-deal expectation.

Algorithm~\ref{alg:advi} is a simplified version from \cite{kucukelbir2017automatic}, benefited that we don't need transform
the support of restricted variable to unconstrained space.

@@

The ADVI use noised gradient to find posterior expect that is equal to MAP(with more low effiecency),
 and collect gradient shock and concussion to estimate posterior variance.

In this paper, meanfield normal approximation is employed. That is:

@@

Where $p(x^E_i \mid D) \sim N(\mu_{x^E_i},\sigma_{x^E_i}^2)$. 
Such $\mu_{x^E_i},\sigma_{x^E_i}^2)$ are called variational(approximated) parameters. 
it's called meanfield since the covariace matrix is a diagonal matrix, 
excluding all of correlation between randomized parameters.

@@

Variational inference is only a approximating method, 
sampling from posterior distribution directly is exact but resource expensive method. 
Classic Hasting-Metropolis method rely on a proposed distribution manually specified by statistician
and suffer bad converge effciency. 
The Hamiltonian Monte Carlo \cite{hoffman2014no} (See Algorithm~\ref{alg:hmc}) can be employed to improve the effciency,
using gradient information instead of proposed distribution to give next step in random walking.

@@

HMC follow the same way as ADVI using gradient pulse and bounce.

HMC and other sampling method return a "trace" sample that can be used 
to build empirical posterior distribution. In this paper, the trace almost always been see as
parameters of normal distribution to compare to VB(ADVI) thougn it drop the main advantage of sampling method.

@@

\section{Inference experiments 推断实验}

\subsection{Enemy position detecting 敌军位置探测}

The situation (see Figure~\ref{fig:expState}) will be used as inference experiment data.

@@

Firstly, if flat prior is used (only provide likelihood), the MAP result is Figure~\ref{fig:MAPone}.

@@

The arrowtail indicate the "true" position of enemy(though it can't be seen), 
the arrowhead indicate the estimated position of enemy for MAP. As we can see,
a enemy is pulled to the back of ally units to maximize probability, it seems overfit anyway.
We can utilize the advatage of bayes framework, adding a prior \footnote{Or regulation term, but I
prefer the probability meaning offered by bayes.}:

@@

Where $t$ is tense parameter for enemy position,
$\alpha$ is corresponding threshold. We set $t=5.0,\alpha=5.0$
for illustration below.

The new joint probability with the diagonal prior is:

@@

Where $N_B,N_E$ are number of battle and enemy,$x^B_i,y^B_i$ is coordinate of battle $i$, $x^E_j,y^E_j$
is coordinate of enemy $j$.

The result of MAP on the new probability function looks better as shown in the Figure~\ref{fig:MAPtwo}.

@@

\subsubsection{Sampling and Variational inference 采样和变分推断}

Point estimation is not enough since it can't give uncertain information about the estimation.
Tough exact posterior may fix it but it's hard to compute and represent. Two ways in bayes inference 
to do it are sampling and variational inference(VI). The former one generate a "trace" which can be thought
as a sample taken from exact posterior, the trace may contitude empirical distribution or reveal 
attribution of the random parameter. The VI is faster but lack exact attribution.

The two results of VI in flat prior and new diagonal prior can be seen in Figure~\ref{fig:VI}.
The two results of sampling can be seen in Figure~\ref{fig:samping}.

@@

@@

Where the coordinate of ellipses indicate the expectation of those posterior distribution,
and the radius of ellipses indicate the standard deviation(sd) of axis x and y in every latent enemy point.
So those ellipse can be seen as a rough approximation for posterior distribution 
hidden in trace or variational distribution, though those two are not exact posterior too.

The HMC result seems inconsisitency, implying the converge fail. Though increasing sample size may be
solution(see Figure~\ref{fig:SamplingTen}). But just like we are not content to a NP-hard solver and claim that it only need more time,
sampling seems too weak in this problem.

@@

\subsection{Mutiple enemy number setting 变化敌人数量设定}

The above estimation is based on "true" number of enemy. Let we test its stability. 
What happen if the given number of number of enemy is wrong? The Figure~\ref{fig:bigVb} 
show the result, that flat prior seems well while diagonal prior may may be dominated by 
the prior. But it depict what we want in general.

@@

\subsubsection{The density of probabity of existence of enemy estimation 敌人存在性概率密度估计}

The one of advantage of VB is that it make computation of probability of specific region very easy.
The probability of exist of enemy in a given region $[x,x+dx]\times[y,y+dy]$ can be given by:

@@

Where $\Phi(x)$ is standard cumulative probability function:

@@

And $\mu^X_i$ is the expect parameter of normal approximated posterior probability of ith enemy.
The three other are same.

The existence density(approximated) is defined:

@@

Where $\epsilon$ is a small number, in there $\epsilon=0.01$. 
The two example can be seen in Figure~\ref{fig:existDensity}. 
The comparing result can be seen in seen in Figure~\ref{fig:bigVbExist}.

@@

\section{Extention: Enemy movement detecting 扩展：敌方运动检测}

Considering ally,enemy,battles have not only positions, but also have timestamp. In another word,
enemy and ally may move in a time range, how do we infer the movement?

Interestingly, the model requires only a bit of modifications to integrate the new specification.

Assurming the time begin at $0$ and end at $1$, and enemy have uniform motion in constant speed.
So the parameters$x^E_i$ can be rewritten as $x^E_i(t) = (1-t)x^E_i(0) + tx^E_i(1)$, 
where $x^E_i(0),x^E_i(1)$ means the positions of ith enemy in time 0 and 1 respectively, and so on.
They are new parameters. The other structual probability function almost keep its original form.

First, assurming $x^E_i(0),y^E_i(0)$ are known and $x^E_i(1),y^E_i(1)$ are unknown.
A instance of inference is shown in Figure~\ref{fig:bkeu}. 
Where arrowtail indicate the known begin point.
The one of two arrowhead surrounded by sd ellipse is estimated $t=1$ coordination expectation. 
The another one is "true" target point.

@@

The following Figure~\ref{fig:bueu} show the situation in which $t=0,1$ situation are both unknown
\footnote{Note they're not in same data set.}. Where the arrowtail of first arrow is "true" begin
point, the middile point is estimated posterior expect of the point at $t=0$, the arrowhead of second arrow
is estimated posterior expect of the point at $t=1$.

@@

The prior that give punishment to too long moving range also are useful and easy to implement. 
But the dataset that can highlight the advantage don't be constructed yet subject to time limit.
So it will be skiped.

@@

\section{Extention: Dealing complex position distribution. 扩展：处理复杂的复杂的分布形状}

The above contents are based on similar distribution, a curve can divide ally and enemy easily.
What will happen if the shape become complex and hard to capture for "one center" bayes naive classifer?

@@

\subsection{Circle 圆形}

The "true" position is droped. This section will contain only "initialization value"
(In above content, "true position" play also initialization value role.). 
The Figure~\ref{fig:circleIteration} show the circle setting with flat prior, 
showing also a nice iteration convege process .

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{circle_iteration.png}
\caption{Iteration process for circle setting with flat prior and random initialization
均匀先验+圆形设定+随机初始化下的迭代收敛过程}
\label{fig:circleIteration}
\end{figure}

\subsection{Case study: The battle of Gettysburg 案例研究：葛底斯堡战役}

Now, it's the time to abandon the globular chicken in vacuum loved by physicists.
The Figure~\ref{fig:gettysburg} show the map and corresponding data of the battle of Gettysburg in second day.
The data only capture the division(NATO:XX) and bridge brigade(NATO:X) in the map.
\footnote{You may aware the top right corner is not matched well. 
That is because The data depict state in morning and the map draw the situation in afternoon, the main battle time.
So it miss the march time the former one may infer.}
The confederate army have less number of divisions since the size of the divisions of CSA are more big.
The data is from HPS great wargame "Civil war:Gettysburg". 
The data used are listed in the Table~\ref{tab:Confederate} and \ref{tab:Union}, in which strength 
is number of unit that is not used in the model yet and will be used in later section as weight.

@@

\begin{table}
\parbox{.45\linewidth}{
\begin{tabular}{lrrr}
\toprule
{} &  strength &    x &    y \\
\midrule
Heth's Div     &      4628 &  2.4 &  4.8 \\
McLaws' Div    &      6762 &  2.9 &  1.0 \\
Hood's Div     &      6957 &  3.3 &  0.1 \\
Anderson's Div &      6686 &  3.5 &  2.8 \\
Pender's Div   &      5080 &  3.6 &  3.7 \\
Rodes' Div     &      5202 &  5.0 &  4.2 \\
Early's Div    &      4572 &  6.0 &  3.9 \\
Johnson's Div  &      6012 &  7.2 &  4.5 \\
\bottomrule
\end{tabular}
\caption{Confederate oob}
\label{tab:Confederate}
}
\hfill
\parbox{.45\linewidth}{
\begin{tabular}{lrrr}
\toprule
{} &  strength &    x &    y \\
\midrule
2nd D (Humphreys)   &      4913 &  4.2 &  1.7 \\
1st Div (Birney)    &      5008 &  4.5 &  0.8 \\
2nd Div (Gibbon)    &      3558 &  5.1 &  2.3 \\
3rd Div (Hays)      &      3622 &  5.2 &  2.6 \\
1st Div (Caldwell)  &      3303 &  5.2 &  1.8 \\
3rd Div (Schurz)    &      1633 &  5.3 &  3.1 \\
2nd Div (Steinwehr) &      2264 &  5.4 &  2.9 \\
3rd Div (Doubleday) &      2922 &  5.4 &  2.7 \\
1st Div (Barlow)    &      1475 &  5.5 &  3.1 \\
2nd Div (Robinson)  &      1311 &  5.5 &  2.6 \\
1st Div (Wadsworth) &      1697 &  6.2 &  3.0 \\
2nd Div (Geary)     &      3851 &  6.2 &  2.8 \\
1st Div (Williams)  &      4698 &  6.3 &  2.1 \\
2nd Div (Ayres)     &      3990 &  6.6 &  1.6 \\
1st Div (Barnes)    &      3411 &  6.7 &  1.7 \\
3rd Div (Crawford)  &      2842 &  6.8 &  1.6 \\
3rd Div (Newton)    &      4729 &  7.3 &  0.8 \\
1st Div (Wright)    &      4181 &  7.4 &  1.2 \\
2nd Div (Howe)      &      3548 &  9.3 &  0.0 \\
\bottomrule
\end{tabular}
\caption{Union oob}
\label{tab:Union}
}
\end{table}

Following we assurm the position of army of Union and battle are known but CSA not.

@@

In Figure~\ref{fig:gettysburgTwo} the forward probability model is illustrated and a sample of the model and observed
ally unit.

@@

We can run procedure described above with randomized initialized point. 
Figure~\ref{fig:gettysburgInit} show the exist-probability and converge process.

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{gettysburg-init.png}
\caption{Iteration process for randomized initialized setting with flat prior in Gettysburg sample
均匀先验+随机初始化变分推断在葛底斯堡数据上的迭代过程}
\label{fig:gettysburgInit}
\end{figure}

It looks good, thougn the enemy units seems too close to ally. It can be solved a bit by prior.

@@

\section{Extention: Size effect 扩展：规模相关模型}

The above content assurms battles and units are homogeneous. It may make sense,
but if battle and unit can include number and size information, the result will be more useful.

To extend our model to embrace the change, we can merely define the high weight the unit have,
the long radius in distance factor and large weight in estimation on center of class unit cause.

Following content use the strength of Table~\ref{tab:Confederate} and \ref{tab:Union} as weight.
The $\mu,\sigma$ used by naive bayes classifer is computed by weithted version now.
And the distance will be adujusted to $dist_{ij} = dist_{ij} \frac{\beta}{stre_i}$, the $\beta$
is seted to $6000$. So all of units of Union will be penalized, 
and a few of Confederate will be bonused for distance factor.

The Figure~\ref{fig:gettysburgInitTwo} show the result, it very like the result fited without size effect. 
It turn out that the model is steady for suct effect.

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{gettysburg-init2.png}
\caption{Iteration process for randomized initialized setting with flat prior with Size effect
规模效应+随机初始化+均匀先验的迭代过程}
\label{fig:gettysburgInitTwo}
\end{figure}

\section{Conclusion 结论}

We present a standard bayes inference framework 
\footnote{In fact, the content of the paper have been implmented as examples of a open-source library
hosted in GitHub, see: \url{https://github.com/yiyuezhuo/bayes-torch} where yiyuezhuo is the nickname of
the writer Yueyi Zhuo} 
in a classes of prolbem in which 
two class of point(ally and enemy) will generate another class of points(battle), 
when one class is hidden(enemy).

The forward model can transformed easily to backward model to do inference due to our framework.
The inference include point detection, movement dectection with prior or adujusted prior.
They're be checked its steady and converge performance by true initialization and random initialization.
A case study about battle of Gettysburg summary the content covered by the paper. 
I wish the result can be producation environment and my game desigmning.

Desigmning the forward model, doing its inference and balancing effciency and correctness 
are interesting challenge, but useful.

@@

\section{Core code implementing the model 实现模型的主要代码}

This code section contain only the component defining the baseline model and do inference. 
The full code about figure outputing, parameter tuning and model variants code can be checked in 
\footnote{\url{https://github.com/yiyuezhuo/Undergraduate-thesis/tree/master/notebook}}.

@@

The top code on baseline model:

@@

The movement detecting model variant:

@@

The weighted model variant about forward and backward:

@@

There're bayes-torch related code.

Class Model, defining the methods to do point estimation, vb and sampling.

@@

Other helper function in bayes-torch:

@@

>>>>

\usepackage{verbatim} % for block comment

@@

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{SmolenskR4.jpg}
\caption{
图中展示了经典兵棋公司HPS的作品斯摩棱斯克41对侦查的处理——单位仅能出于完全可知和完全不可知的状态。 }
\label{fig:hps}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{metz.jpg}
\caption{
梅兹战役地图，地图展示了并不应该在真实战场上所能看到的OOB }
\label{fig:metz}
\end{figure}

@@

@@

\begin{figure}[ht]
\includegraphics{state_no_battle.png}
\caption{
友军和敌军的位置设定}
\label{fig:stateNoBattle}
\end{figure}

@@

@@

@@

@@

\begin{figure}[ht]
\includegraphics{state_no_battle_prob.png}
\caption{战役发生概率密度分布}
\label{fig:stateNoBattleProb}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{gridify.png}
\caption{$25 \times 25$ 离散近似}
\label{fig:gridify}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{state_sample_battle.png}
\caption{敌友军，战役概率与一个特定战役样本}
\label{fig:stateSampleBattle}
\end{figure}

这时如果把敌人的位置隐去，就可以得到实际推断中所用的数据，如图~\ref{fig:stateNoEnemy}。
类似频率主义稻草人式讨论，可以通过比较生成过程隐去的真实值与推断的值来判定推断的效能。

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{state_no_enemy.png}
\caption{隐藏敌人后，实际推断时所能看到的信息}
\label{fig:stateNoEnemy}
\end{figure}

@@

@@

@@

@@

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{naivebayes.png}
\caption{朴素贝叶斯分配器预测概率等高线图}
\label{fig:naivebayes}
\end{figure}

@@

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb1.png}
\caption{
组合朴素贝叶斯分类器与平滑的距离因子后的战斗概率}
\label{fig:combOne}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb2.png}
\caption{过于分散的样本}
\label{fig:combTwo}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb4.png}
\caption{
当扩大讨论范围后，不合理的样本不可避免地出现}
\label{fig:combThree}
\end{figure}

\subsection{使用的基线模型}

%We assign a point constant probability 
%if it is greater than conflict threshold and less than distance threshold:

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb5.png}
\caption{
强制0概率可以解决不合理点的麻烦}
\label{fig:combFive}
\end{figure}

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.6\linewidth]{comb6.png}
\caption{基线模型}
\label{fig:combSix}
\end{figure}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\section{推断实验}

\subsection{敌军位置探测}

@@

@@

@@

@@

@@

\subsubsection{采样和变分推断}

@@

分别采用均匀先验和对角先验两次变分推断拟合结果见图~\ref{fig:VI}。

分别采用均匀先验和对角先验两次采样结果见图~\ref{fig:samping}。

@@

@@

\subsection{变化敌人数量设定}

@@

\subsubsection{敌人存在性概率密度估计}

@@

@@

@@

@@

\section{扩展：敌方运动侦测}

@@

@@

@@

\section{扩展：处理复杂的复杂的分布形状}

@@

\subsection{圆形}

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{circle_iteration.png}
\caption{
均匀先验+圆形设定+随机初始化下的迭代收敛过程}
\label{fig:circleIteration}
\end{figure}

\subsection{案例研究：葛底斯堡战役}

@@

\begin{table}
\parbox{.45\linewidth}{
\begin{tabular}{lrrr}
\toprule
{} &  strength &    x &    y \\
\midrule
Heth's Div     &      4628 &  2.4 &  4.8 \\
McLaws' Div    &      6762 &  2.9 &  1.0 \\
Hood's Div     &      6957 &  3.3 &  0.1 \\
Anderson's Div &      6686 &  3.5 &  2.8 \\
Pender's Div   &      5080 &  3.6 &  3.7 \\
Rodes' Div     &      5202 &  5.0 &  4.2 \\
Early's Div    &      4572 &  6.0 &  3.9 \\
Johnson's Div  &      6012 &  7.2 &  4.5 \\
\bottomrule
\end{tabular}
\caption{南方邦联军编制}
\label{tab:Confederate}
}
\hfill
\parbox{.45\linewidth}{
\begin{tabular}{lrrr}
\toprule
{} &  strength &    x &    y \\
\midrule
2nd D (Humphreys)   &      4913 &  4.2 &  1.7 \\
1st Div (Birney)    &      5008 &  4.5 &  0.8 \\
2nd Div (Gibbon)    &      3558 &  5.1 &  2.3 \\
3rd Div (Hays)      &      3622 &  5.2 &  2.6 \\
1st Div (Caldwell)  &      3303 &  5.2 &  1.8 \\
3rd Div (Schurz)    &      1633 &  5.3 &  3.1 \\
2nd Div (Steinwehr) &      2264 &  5.4 &  2.9 \\
3rd Div (Doubleday) &      2922 &  5.4 &  2.7 \\
1st Div (Barlow)    &      1475 &  5.5 &  3.1 \\
2nd Div (Robinson)  &      1311 &  5.5 &  2.6 \\
1st Div (Wadsworth) &      1697 &  6.2 &  3.0 \\
2nd Div (Geary)     &      3851 &  6.2 &  2.8 \\
1st Div (Williams)  &      4698 &  6.3 &  2.1 \\
2nd Div (Ayres)     &      3990 &  6.6 &  1.6 \\
1st Div (Barnes)    &      3411 &  6.7 &  1.7 \\
3rd Div (Crawford)  &      2842 &  6.8 &  1.6 \\
3rd Div (Newton)    &      4729 &  7.3 &  0.8 \\
1st Div (Wright)    &      4181 &  7.4 &  1.2 \\
2nd Div (Howe)      &      3548 &  9.3 &  0.0 \\
\bottomrule
\end{tabular}
\caption{联邦军编制}
\label{tab:Union}
}
\end{table}

@@

@@

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{gettysburg-init.png}
\caption{
均匀先验+随机初始化变分推断在葛底斯堡数据上的迭代过程}
\label{fig:gettysburgInit}
\end{figure}

@@

\section{扩展：考虑规模效应模型}

@@

\begin{figure}[ht]
\includegraphics[width=0.99\linewidth]{gettysburg-init2.png}
\caption{
规模效应+随机初始化+均匀先验的迭代过程}
\label{fig:gettysburgInitTwo}
\end{figure}

\section{结论}

@@

%\begin{comment}

\section{实现模型的主要代码}

@@

@@

@@

@@

@@

@@

%\end{comment}
